\sysfull

### 2018-04-13 paper/evaluation.tex
complier removed from evaluation results

%We present the experimental results of \sys's performance. We start with describing the hardware environment (Section~\ref{sec:results_hardware}) followed by the software environment (Section~\ref{sec:results_software}) and we concluded by the evaluation results (Section~\ref{sec:results_evaluation}).

We evaluated \sys using a WISP\,5.1~\cite{wisp5,wisp} energy-harvesting platform build around a MSP430FR5969~\cite{wolverine} MCU with 64\,kB of FRAM. We used a TI Flash Emulation Tool (FET)~\cite{fet} as a power supply during experiments with continuous power. For energy measurements, we used EDB~\cite{edb}. In experiments with wireless power, we powered the WISP using an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. We controlled the RFID reader from a workstation running Ubuntu 10.4 using \emph{sllurp}~\cite{sllrp_github}. We set the transmitted power of the RFID reader to 30\,dBm at 915\,MHz center frequency. For distance-controlled experiments, we affixed the WISP at varying lengths to hollow paper tubes placed flat on a lying antenna. Timing measurements were done using the Salea~\cite{saleae} logic analyzer.

For some experiments (noted below) we used an alternative setup where the MSP-TS430RGZ48C launchpad was used for continuous power experiments and used internal timer for measuring run time. For harvested energy, we used WISP\,5.0~\cite{wisp5,wisp} hardware and ThingMagic Astra-EX integrated RFID reader set at 30\,dBm transmission power at 915\,MHz. We used EDB~\cite{edb} to measure run time. Applications were cross-compiled using GCC and Clang (both version 3.8.0), allowing us to use LLVM for the \sys compiler.

\subsection{Benchmarks and Baseline}
\label{sec:results_software}

%We compare \sys against state-of-the-art task-based runtime Alpaca~\cite{alpaca}. We do not compare \sys against Chain~\cite{chain}, another task-based system, which is inferior to Alpaca in its performance. Also, we do not compare \sys to checkpointing-based systems, such as DINO~\cite{dino} or Mementos~\cite{mementos} (cf. Section~\ref{sec:background_consistency}), as both of them are build on top LLVM compiler, which performance is inferior to GCC compiler used in the evaluation of \sys \todo{Please check if the LLVM compiler argument makes sense}.

%We evaluated \sys using benchmarks that originated from the MiBench testing suite~\cite{mibench,hicks_mibench2_2016}. Specifically, we have implemented three benchmarks used by Chain~\cite{chain} and Alpaca~\cite{alpaca} (source code: \cite{coala_website}), namely: \textbf{ar}: nearest neighbor classification of randomly generated data modeling a three-axis accelerometer; \textbf{bc}: counts bits in byte pseudo-random string using several algorithms, and compares results for correctness; \textbf{cuckoo}: Bloom-filter-like Cuckoo filter that first hashes a sequence of pseudo-random numbers, then queries the filter to recover the sequence. Additionally, we have ported three new benchmarks from~\cite{mibench}, namely: \textbf{fft}: Fast Fourier Transform algorithm \todo{specify details of the implementation}; and \textbf{sort}: selection sort algorithm on a fixed sequence of numbers. \todo{justify the selection of these benchmarks} All applications are summarized in Table~\ref{table:compiler_result} in terms of memory footprint, source lines of code and number of tasks. \todo{update table with new data}

@@

\subsubsection{\sys's Compiler}
\label{sec:result_compiler_time}

@@

\textbf{\sys Compiler Generated Code Characterization.} The behaviour and the efficiency metrics of the \sys compiler are given in Table~\ref{table:compiler_result}.  \todo{update table with new data}
%
%for each application, for manually written (Man.) and automatically compiled (Comp.) benchmarks the difference in the number of bytes of protected data (columns 2 and 3), the number of tasks (columns 4 and 5), the number of \sys protected data API access calls (columns 6 and 7), the lines of code in each application for \sys and Chain (columns 8 and 9), and compilation time using \sys's compiler (column 10).
%
On average, compiler-generated code introduces about 0.3\% more bytes of protected data, suggesting that liveness analysis captures natural boundaries in the use of variables also caught by a manual implementation. Compiler-generated code generates about 16\% fewer tasks for applications, on average. The results indicate that the \sys compiler selects task boundaries differently than a programmer would manually, favoring fewer, larger tasks. The \sys compiler inserts protected data access operations conservatively when a variable {\em may} alias a protected variables, due to the limitations of pointer aliasing. Consequently, the \sys compiler introduces 48\% more protected data accesses than programmer-written code. The run time results in Section~\ref{sec:result_compiler_time} show that the increase in protected data
accesses sometimes degrades performance. Overall, the data show that the compiler automatically generates tasks similarly to manually written tasks. Doing so, \sys's compiler reaps the static task benefits of \sys, but simplifies programming by sparing the programmer the job of task decomposition.

\textbf{Compile Time.} We measured compile time for \sys's compiler's automatic task generation for each application\footnote{We could not compile the dft application since LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the applications on a 4-core virtual machine with 1\,GB of memory running Arch Linux on an Intel Core i5-6200U at 2.30\,GHz. We collected results using the Linux system time collected in seconds. Most of the compile time was spent computing pointer alias analysis, while calculating the possible live ranges of variables. Applications such as rsa that have a larger code size and manipulate more variables have a longer compilation time, due to a larger search space for pointer aliasing. Nonetheless, the compile time is orders of magnitude shorter than manually defining tasks, which requires hours of programmer time. %The characterization of \sys's compiler suggests that the \sys compiler enables simpler task-based intermittent programming for \sys.

\textbf{Run Time of \sys Compiler Code.} In addition to the characterization of the \sys compiler in Table~\ref{table:compiler_result}, we experimentally assessed the performance of the \sys compiler, compared to the performance of the manually written benchmarks, as written in prior work~\cite{alpaca,chain}. Figure~\ref{fig:comp_user} compares the performance of manually written benchmark code to the performance of code automatically compiled using \sys. The figure shows run time for both cases, normalized to the run time of the manually written program, running on continuous power. The data show that in all cases except for ar and rsa, the run time performance of compiled code generated by the \sys compiler has comparable performance to manually written code. With comparable performance in most cases, the data suggest that the \sys compiler not only makes programming simpler, but does so, in most cases, without a high run time overhead. In the cases of both ar and rsa, the code manipulates a large amount of data that is stored in an array and passed into functions by reference. We expect that the data being manipulated by reference is leading to a large amount of may-alias references in the compiler's analysis, which leads to a larger number of accesses to protected data in the automatically compiled code, compared to the manually written code.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/comp_user}
	\caption{\textbf{\sys compiler code overhead measured in terms of execution time per application} (dft excluded as it was not compiled by \sys compiler, see Table~\ref{table:compiler_result}); WISP was powered continuously.}
	\label{fig:comp_user}
\end{figure}

>>>>

@@

%\subsubsection{\sys's Compiler}
%\label{sec:result_compiler_time}

@@

%\textbf{\sys Compiler Generated Code Characterization.} The behaviour and the efficiency metrics of the \sys compiler are given in Table~\ref{table:compiler_result}.  \todo{update table with new data}
%
%for each application, for manually written (Man.) and automatically compiled (Comp.) benchmarks the difference in the number of bytes of protected data (columns 2 and 3), the number of tasks (columns 4 and 5), the number of \sys protected data API access calls (columns 6 and 7), the lines of code in each application for \sys and Chain (columns 8 and 9), and compilation time using \sys's compiler (column 10).
%
%On average, compiler-generated code introduces about 0.3\% more bytes of protected data, suggesting that liveness analysis captures natural boundaries in the use of variables also caught by a manual implementation. Compiler-generated code generates about 16\% fewer tasks for applications, on average. The results indicate that the \sys compiler selects task boundaries differently than a programmer would manually, favoring fewer, larger tasks. The \sys compiler inserts protected data access operations conservatively when a variable {\em may} alias a protected variables, due to the limitations of pointer aliasing. Consequently, the \sys compiler introduces 48\% more protected data accesses than programmer-written code. The run time results in Section~\ref{sec:result_compiler_time} show that the increase in protected data accesses sometimes degrades performance. Overall, the data show that the compiler automatically generates tasks similarly to manually written tasks. Doing so, \sys's compiler reaps the static task benefits of \sys, but simplifies programming by sparing the programmer the job of task decomposition.

%\textbf{Compile Time.} We measured compile time for \sys's compiler's automatic task generation for each application\footnote{We could not compile the dft application since LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the applications on a 4-core virtual machine with 1\,GB of memory running Arch Linux on an Intel Core i5-6200U at 2.30\,GHz. We collected results using the Linux system time collected in seconds. Most of the compile time was spent computing pointer alias analysis, while calculating the possible live ranges of variables. Applications such as rsa that have a larger code size and manipulate more variables have a longer compilation time, due to a larger search space for pointer aliasing. Nonetheless, the compile time is orders of magnitude shorter than manually defining tasks, which requires hours of programmer time. %The characterization of \sys's compiler suggests that the \sys compiler enables simpler task-based intermittent programming for \sys.

%\textbf{Run Time of \sys Compiler Code.} In addition to the characterization of the \sys compiler in Table~\ref{table:compiler_result}, we experimentally assessed the performance of the \sys compiler, compared to the performance of the manually written benchmarks, as written in prior work~\cite{alpaca,chain}. Figure~\ref{fig:comp_user} compares the performance of manually written benchmark code to the performance of code automatically compiled using \sys. The figure shows run time for both cases, normalized to the run time of the manually written program, running on continuous power. The data show that in all cases except for ar and rsa, the run time performance of compiled code generated by the \sys compiler has comparable performance to manually written code. With comparable performance in most cases, the data suggest that the \sys compiler not only makes programming simpler, but does so, in most cases, without a high run time overhead. In the cases of both ar and rsa, the code manipulates a large amount of data that is stored in an array and passed into functions by reference. We expect that the data being manipulated by reference is leading to a large amount of may-alias references in the compiler's analysis, which leads to a larger number of accesses to protected data in the automatically compiled code, compared to the manually written code.

%\begin{figure}
%	\centering
%	\includegraphics[width=\columnwidth]{figures/comp_user}
%	\caption{\textbf{\sys compiler code overhead measured in terms of execution time per application} (dft excluded as it was not compiled by \sys compiler, see Table~\ref{table:compiler_result}); WISP was powered continuously.}
%	\label{fig:comp_user}
%\end{figure}
